|

### 2021-12-14 front-and-back-matter/_acknowledgements.Rmd
Update acknowledgements and dedication

This thesis would not have been possible with Ciara Gardiner. Lots of people say that at this point in the Acknowledgements, but I mean it literally. Between here managing.

The person I have loved with all my heart

Without here

Finally, deepest thanks to Ciara Gardiner: holder-of-forts, maker-of-spreadsheets, and all-round fiancee-extraordinaire. I can't wait for the next adventure with you.

@@

On a personal note, there are several people without whom I would not have survived the process of writing a dissertation during COVID times.

Thank also to Doug for introducing me to the joys of running, Ben for always being around to chat, and Christin for encouraging regular coffee-breaks.

Thanks to Mum and Dad for your never-ending love and support, and everything they have done to get me to point there doing and submitting a thesis.

>>>>

This thesis would not have been possible with Ciara Gardiner. Lots of people say this about someone at this point in the acknowledgements, and I'm always sceptical of whether it is true, so to avoid any doubt I mean it here quite literally.

Ciara, I'd need (at least) another <<words>> words to accurately describe all the ways in which you supported me through this endeavour. It can't have been fun being locked-down in a small flat with a grumpy and stressed PhD student, nor trying to support the same student remotely from Dublin. I talk about lessons learnt during this thesis in the Discussion, but the biggest takeaway for me is that I am incredibly lucky to have found you and to get to take on life while holding your hand. Thank you and I love you.

Thanks to Mum and Dad for your never-ending love and support, and everything they have done to get me to point where doing and submitting a thesis.

@@

On a personal note, there are several people without whom I would not have survived the process of writing a dissertation during COVID times. Ben, Doug, Christin - thank you!

### 2021-12-14 index.Rmd
Update acknowledgements and dedication

author: Luke A McGuinness
college: 
degree: Doctor of Philosophy
degreedate: December 2021
word-count: |
  `r read.csv("data/words/words.csv") %>% dplyr::pull(1) %>% dplyr::last() %>% comma()`
abstract: |
  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
acknowledgements: |
  `r paste(readLines("front-and-back-matter/_acknowledgements.md"), collapse = '\n  ')`
declaration: |
  `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
dedication: For Brendan McHugh
covidStatment: |
  `r paste(readLines("front-and-back-matter/_covidStatment.Rmd"), collapse = '\n  ')`
abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations

>>>>

author: Luke A McGuinness
college: 
degree: Doctor of Philosophy
degreedate: December 2021
word-count: |
  `r read.csv("data/words/words.csv") %>% dplyr::pull(1) %>% dplyr::last() %>% comma()`
abstract: |
  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
acknowledgements: |
  `r paste(readLines("front-and-back-matter/_acknowledgements.md"), collapse = '\n  ')`
declaration: |
  `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
dedication: |
  `r paste(readLines("front-and-back-matter/_dedication.Rmd"), collapse = '\n  ')`
covidStatment: |
  `r paste(readLines("front-and-back-matter/_covidStatment.Rmd"), collapse = '\n  ')`
abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations
